The Skew-Normal Approximation of the Binomial Distribution

### 2011-01-22 project/paper/method-of-moments.tex
Wording tweaks.

Let's start with the binomial. The first two central moments are simply the
mean and variance, which we can state from memory:

@@

Having these, we can easily find $E(B^2)$: Recall that $Var(B) = E(B^2) -
[E(B)]^2$ and thus

\begin{equation*}
  E(B^2) = Var(B) + [E(B)]^2 = np(1-p) + n^2p^2 = np - np^2 + n^2p^2,
\end{equation*}

a fact we will need for the third central moment.

@@

Now, finally, we have all the building blocks necessary to obtain the third
central moment:

>>>>

Let's start with the binomial. The first two central moments are simply the
mean and variance:

@@

From these, we can find $E(B^2)$: Recall that $Var(B) = E(B^2) - [E(B)]^2$ and
thus

\begin{equation*}
  E(B^2) = Var(B) + [E(B)]^2 = np(1-p) + n^2p^2 = np - np^2 + n^2p^2.
\end{equation*}

@@

Now, finally, we have all the information necessary to obtain the third central
moment:
